Our Title

### 2015-05-03 draft.tex
Added in Grant's Section 6.2.3, on Domestic Portal and Border Monitoring.

\usepackage{caption}  % Use for \captionof(*) command
\usepackage{pdfpages}

@@

@@

@@

@@

@@

@@

@@

>>>>

\usepackage{caption}  % Use for \captionof(*) command
\usepackage{subcaption}
\usepackage{pdfpages}

@@

AAPA - American Association of Port Authorities

@@

ASP - Advanced Spectroscopic Portal Monitor

CBP - U.S. Customs and Border Protection

@@

DNDO - Domestic Nuclear Detection Office

@@

ICE - Immigration and Customs Enforcement

@@

PNNL - Pacific Northwest National Lab

@@

RPM - Radiation Portal Monitor

@@

\subsection{Domestic Portal and Border Monitoring}

\subsubsection{??????  Needs content proofing ???????}

As with any foreign terrorist threat, it is imperative to assess the United States' domestic capabilities for the detection and interception of weapons and materials that pose a significant risk to American security. In the context of this section, we specifically consider nuclear weapons and materials that have the potential to be detonated domestically after being smuggled past American borders. We examine current and past efforts and capabilities to prevent such weapons from entering the United States undetected, as well as the possibilities for the development and implementation of better detection technologies.

Two of the relevant governmental organizations regulating domestic borders and security are the Federal Bureau of Investigation (FBI) and the Department of Homeland Security (DHS). Together, these organizations are responsible for the security of the United States against both domestic and foreign threats. They coordinate intelligence gathering as well as threat-response and eventually coordinate with the justice system. With these goals in mind, a significant portion of their work deals with the monitoring of borders. The Department of Homeland Security alone commands more than 180,000 personnel, operating such sub-groups as the U.S. Coast Guard, U.S. Customs and Border Protection (CBP), and the Immigration and Customs Enforcement (ICE) \cite{Robb2005}. One of the most relevant DHS sub-groups is the Domestic Nuclear Detection Office (DNDO). The DNDO is responsible for the development and deployment of radiation and detection equipment to assist any other federal agency, including the other DHS sub-organizations and the FBI \cite{UnitedStatesGovernmentAccountabilityOffice2013}.

The aforementioned government agencies have correctly addressed border and seaport monitoring as a location of high potential for the interception and detention of nuclear weapons and materials. In 2005, the CBP in collaboration with the American Association of Port Authorities (AAPA) had already begun deployment of a large network of Radiation Portal Monitors (RPMs) with a comprehensive plan for 100\% screening of the locations seen in \autoref{fig:RPM_map} \cite{Simmons2005}.

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.55]{./figures/RPM_map.png}
   \caption{CBP plan for RPM deployment \cite{Simmons2005}.}
     \label{fig:RPM_map}
\end{figure}

The CPB/AAPA RPM plan outlines a phased implementation targeting locations on a priority basis around the U.S. The plan additionally details a technology collaboration with the Pacific Northwest National Lab (PNNL), who was responsible for the development of cutting-edge, harmless and passive detection systems (illustrated in \autoref{fig:RPM_designs}). In 2005, RPM systems had already been deployed at 14 terminals, with another 18 in construction and 27 in final design \cite{Simmons2005}.

\begin{figure}
        \centering
        \begin{subfigure}[b]{0.3\textwidth}
                \includegraphics[width=\textwidth,scale=1]{./figures/fixed_vehicle.png}
                \caption{Fixed  vehicle monitor.}
                \label{fig:fixed_vehicle}
        \end{subfigure}%
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \includegraphics[width=\textwidth,scale=1]{./figures/mobile_cargo.png}
                \caption{Mobile cargo monitor.}
                \label{fig:mobile_cargo}
        \end{subfigure}
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \includegraphics[width=\textwidth,scale=1]{./figures/perm_train.png}
                \caption{Permanent train monitor.}
                \label{fig:perm_train}
        \end{subfigure}
        \caption{RPM designs and illustrations \cite{Simmons2005}.}\label{fig:RPM_designs}
\end{figure}

Eight years after the initial development of the RPM plan, the Office of the Inspector General published a report documenting the progress made in the RPM development specifically at seaports \cite{DepartmentofHomelandSecurityDHS2013}. The document reports 444 active RPMs screening 99\% of inbound containerized cargo at large seaports, with the other 1\% of cargo entering low-volume seaports (this 1\% presumably not monitored).

One point of concern outlined in the report is that many RPM devices (up to 10\% at a large port) were no longer being used. Further, given the limited use of funds for the DNDO and CBP, no plans (as of the report in 2013) were put in place to ensure continued use of RPM technology. Recommendations were generated in the report to develop an organization to ensure the continued and efficient use of RPMs at seaports.

Development of advanced RPM technologies (meant to replace the old devices) has been continued in recent years, although not necessarily with great success. In 2013, the Government Accountability Office released a report outlining the technical failure of the development of Advanced Spectroscopic Portal Monitors (ASPs) \cite{UnitedStatesGovernmentAccountabilityOffice2013}. Lessons were outlined and documented from the failed attempt at replacement RPMs, but years after the final technology tests. Overall, the entire process was quite cumbersome and ineffective.

In order for the U.S. to be effectively guarded against potential nuclear terrorist threats from cunning organizations such as ISIL, a streamlined, more efficient approach must be taken to portal and border monitoring. True, the initial development and deployment of RPM technology seems to have been fairly effective based on publicly - available reports \cite{Simmons2005,DepartmentofHomelandSecurityDHS2013}. The caveat to these programs is their reported deterioration over a decade of dormancy.

\subsubsection{?????????  Add in cross-reference to below paragraph, once Tech Appendix is made  ??????????? }

This document suggests the aggressive continued advancement of such programs. The continued development of new technologies, as outlined in \autoref{}, must be exploited for every feasible advancement leading to total success in national security. This document suggests a priority-phased plan outlining a strong technological collaboration with government labs, similar to the plan put forth in 2005, in order to develop and deploy the next generation of RPMs \cite{Simmons2005}. Such a plan would be managed by the DNDO and executed by the CPB and AAPA. This plan, however, can only be effective given the successfully executed deployment of any resulting technology. Technological failures such as the ASP development program are acceptable so long as a workable solution is subsequently achieved.
